---
title: "mini-data analysis_1"
author: "Yicheng Wang"
date: "10/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Mini Data Analysis

## Choose datasets 
There are 7 datasets in the datateachr package. Let's first import the two packages,datateachr and tidyverse, needed for analysis.
```{r}
library(datateachr)
library(tidyverse)
```
Before finally choose 4 datasets out of 7, the first 6 rows of each dataset is printed.
```{r}
print(head(apt_buildings))
print(head(building_permits))
print(head(cancer_sample))
print(head(flow_sample))
print(head(parking_meters))
print(head(steam_games))
print(head(vancouver_trees))
```
After seeing the head of dataset, my final decisions are:
*parking_meters
*steam_games
+
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
