---
title: "mini-data analysis_1"
author: "Yicheng Wang"
date: "10/5/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Mini Data Analysis

## Choose datasets 
There are 7 datasets in the datateachr package. Let's first import the two packages,datateachr and tidyverse, needed for analysis.
```{r}
library(datateachr)
library(tidyverse)
```
Before finally choose 4 datasets out of 7, the first 6 rows of each dataset is printed.
```{r}
print(head(apt_buildings))
print(head(building_permits))
print(head(cancer_sample))
print(head(flow_sample))
print(head(parking_meters))
print(head(steam_games))
print(head(vancouver_trees))
```
After seeing the head of dataset, my final decisions are:
*parking_meters
*steam_games
*cancer_sample
*vancouver_trees

Let's narrow down the choice. To do this, we need to do some exploration about the four datasets. We consider to print number of rows and columns, number of numerical columns and 
```{r}
#write a loop to show attributes of parking_meters
a=list(vancouver_trees,parking_meters,steam_games,cancer_sample)
for (val in a)
{
  #cat(as.character(val),"\n")
  cat("The number of rows ",nrow(val),"\n")
  cat("The number of columns ",ncol(val),"\n")
  cat("The number of numeric columns",length(select_if(val,is.numeric)),"\n\n") #calculate the 
}

```
I choose the dataset vancouver_trees
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
